---
title: "NBA API v1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(httr)
library(jsonlite)
library(tidyverse)
library(stringr)
library(plyr)
library(magrittr)
library(lubridate)

```

TODO
    * Players - Add id as first feature for joining to player table (others too?)
    * Season Averages - Automatically query players and join data
    * Teams - Search by city name or team name
    * Games - Reorder
    * Stats - Reorder
    * Season Averages - Reorder

## Package Global Options

```{r}

current_year <- year(today())

year_url <- paste0('https://www.balldontlie.io/api/v1/games?&seasons[]=', current_year) %>% 
  GET()
  
results <- fromJSON(content(year_url, "text"), 
                        flatten = TRUE, 
                        simplifyDataFrame = TRUE) %>% 
   extract2(1)

current_season <- 
  case_when(
    length(results) == 0 ~ current_year - 1,
    TRUE ~ current_year
  )

```


## Players

```{r}

NBA_PLAYERS <- function(search = "", per_page = 100) {
  url <- paste0("https://www.balldontlie.io/api/v1/players", 
                "?",
                "&search=", search,
                "&per_page=", per_page) 
  data <- GET(url)
  
page_count <- fromJSON(content(data, "text"), 
                        flatten = TRUE, 
                        simplifyDataFrame = TRUE)[[2]][[1]]
  
  urls <- list()
  
  for(i in 0:page_count){
    urls[[i+1]] <- paste0(url, "&page=", i)
}
  
all_data <- lapply(urls, GET)
  
combo_data <- list()

for(i in 0:page_count){
  combo_data[[i+1]] <- fromJSON(content(all_data[[i+1]], "text"), 
                        flatten = TRUE, 
                        simplifyDataFrame = TRUE) %>% 
   extract2(1)

}

dataframe <- do.call(rbind,combo_data) %>% 
  as.data.frame() 

 dataframe %>% 
    mutate(height_total_inches = height_feet * 12 + height_inches) %>% 
    relocate(id, 
             first_name, 
             last_name, 
             position, 
             height_feet, 
             height_inches, 
             height_total_inches, 
             weight_pounds) %>% 
   distinct()
}

```

```{r}

data <- NBA_PLAYERS("john") %>% 
  print()

data <- NBA_PLAYERS() %>% 
  print()

```


## Teams

```{r}

NBA_TEAMS <- function(search = "", per_page = 30) {
  url <- paste0("https://www.balldontlie.io/api/v1/teams", 
                "?",
                "&per_page=", per_page) 
  data <- GET(url)
  
  flat_data <- fromJSON(content(data, "text"), 
                        flatten = TRUE, 
                        simplifyDataFrame = TRUE)[[1]]
}

```

```{r}

data <- NBA_TEAMS() %>% 
  print()

```

## Games

```{r}

NBA_GAMES <- function(dates = "", season = "", postseason = "", start_date = "", end_date = "", team_ids = "", per_page = 100) {
  url <- paste0("https://www.balldontlie.io/api/v1/games", 
                "?",
                if_else(dates != "", paste0("&dates[]=", dates), ""),
                if_else(season != "", paste0("&seasons[]=", season), paste0("&seasons[]=", current_season)),
                if_else(postseason != "", paste0("&postseason=", postseason), ""),
                if_else(start_date != "", paste0("&start_date=", start_date), ""),
                if_else(end_date != "", paste0("&end_date=", end_date), ""),
                if_else(team_ids != "", paste0("&team_ids[]=", team_ids), ""),
                "&per_page=", per_page) 
  data <- GET(url)
  
  print(data)
  
page_count <- fromJSON(content(data, "text"), 
                        flatten = TRUE, 
                        simplifyDataFrame = TRUE)[[2]][[1]]
  
  urls <- list()
  
  for(i in 0:page_count){
    urls[[i+1]] <- paste0(url, "&page=", i)
}
  
all_data <- lapply(urls, GET)
  
combo_data <- list()

for(i in 0:page_count){
  combo_data[[i+1]] <- fromJSON(content(all_data[[i+1]], "text"), 
                        flatten = TRUE, 
                        simplifyDataFrame = TRUE) %>% 
   extract2(1)

}

dataframe <- do.call(rbind,combo_data) %>% 
  as.data.frame() %>% 
  distinct()
}

```

```{r}

data <- NBA_GAMES(end_date = "2021-06-05", team_ids = 17, postseason = "TRUE") %>% 
  print()

```


## Stats

```{r}

NBA_STATS <- function(dates = "", season = "", postseason = "", start_date = "", end_date = "", team_ids = "", per_page = 100) {
  url <- paste0("https://www.balldontlie.io/api/v1/stats", 
                "?",
                if_else(dates != "", paste0("&dates[]=", dates), ""),
                if_else(season != "", paste0("&seasons[]=", season), paste0("&seasons[]=", current_season)),
                if_else(postseason != "", paste0("&postseason=", postseason), ""),
                if_else(start_date != "", paste0("&start_date=", start_date), ""),
                if_else(end_date != "", paste0("&end_date=", end_date), ""),
                if_else(team_ids != "", paste0("&team_ids[]=", team_ids), ""),
                "&per_page=", per_page) 
  data <- GET(url)
  
  print(data)
  
page_count <- fromJSON(content(data, "text"), 
                        flatten = TRUE, 
                        simplifyDataFrame = TRUE)[[2]][[1]]

print(page_count)
  
  urls <- list()
  
  for(i in 0:page_count){
    urls[[i+1]] <- paste0(url, "&page=", i)
}
  
all_data <- lapply(urls, GET)
  
combo_data <- list()

for(i in 0:page_count){
  combo_data[[i+1]] <- fromJSON(content(all_data[[i+1]], "text"), 
                        flatten = TRUE, 
                        simplifyDataFrame = TRUE) %>% 
   extract2(1)

}

dataframe <- do.call(rbind,combo_data) %>% 
  as.data.frame() %>% 
  distinct() 
}

```

```{r}

data <- NBA_STATS(postseason = 'TRUE', season = 2020) %>% 
  print()

```


## Season Averages

### Season Averages with Piping

```{r}

NBA_SEASON_AVG <- function(player_ids = ., season = "", per_page = 100) {

  url_ids <- list()
  
    for(i in 1:length(player_ids)){
      url_ids[[i]] <- paste0("&player_ids[]=", player_ids[i])
    }
  
  multi_ids <- url_ids %>% 
    unlist() %>% 
    paste0(collapse = "")
  
      url <- paste0("https://www.balldontlie.io/api/v1/season_averages", 
                  "?",
                  if_else(season != "", paste0("&season=", season), paste("&season=", current_season)),
                  if_else(player_ids != "", multi_ids, ""),
                  "&per_page=", per_page) %>% 
        extract2(1)
    
    data <- GET(url)
    
    print(data)
    
    stats_data <- fromJSON(content(data, "text"), 
                          flatten = TRUE, 
                          simplifyDataFrame = TRUE) %>% 
      extract2(1)
  
  dataframe <- stats_data %>% 
    as.data.frame() %>% 
    distinct() 
}

```

```{r}

player_ids <- c(105)

data <- 
  player_ids %>% 
  NBA_SEASON_AVG() %>% 
  print()

```

## Vignettes

```{r}

stats <- NBA_STATS(season = 2020)


```





## Errors 

The balldontlie API uses the following error codes:

Error Code	Meaning
400	Bad Request -- Your request is invalid.
404	Not Found -- The specified resource could not be found.
406	Not Acceptable -- You requested a format that isn't json.
429	Too Many Requests -- Stop bombarding us.
500	Internal Server Error -- We had a problem with our server. Try again later.
503	Service Unavailable -- We're temporarily offline for maintenance. Please try again later.